COG-ED Manuscript

### 2022-02-17 06_Paper/COG-ED/Manuscript.Rmd

  # define required packages

  packages = c("bibtex", "here", "tidyverse", "bayestestR", "papaja", "lmerTest", "afex", "emmeans", "sjPlot",
               "kableExtra", "interactions", "glmmTMB", "BayesFactor", "ggplot2", "egg", "knitr", "effectsize",
               "MuMIn")

  # check whether each package is installed and install and/or load library

  # the following code does not work for me, gives an error message upon knitting:
  # > trying to use CRAN without setting a mirror
  # removing "papaja" from the list of packages (see below) does not solve the 
  # issue; perhaps we should setup the project using the renv package?

  installed_packages <- packages %in% rownames(installed.packages())
  if (any(installed_packages == FALSE)) {
     install.packages(packages[!installed_packages])
  }
  invisible(lapply(packages, library, character.only = TRUE))

  # papaja must be installed from GitHub so code above will not work for this package
  # Install devtools package if necessary
  # if(!"devtools" %in% rownames(installed.packages())) install.packages("devtools")

  # Install the stable development verions from GitHub
  # devtools::install_github("crsh/papaja")

  # Install the latest development snapshot from GitHub
  # devtools::install_github("crsh/papaja@devel")

@@

  # we will add the package versions before submission

@@

@@

Johnson-Neyman interval:

`r paste("[", round(h2c_jn.int[1], digits = 2), ", ", round(h2c_jn.int[2], digits = 2), "]", sep = "")`

Specification curve analysis:

>>>>

  # load here-library for path-independent project structure (install here by calling install.packages("here") if necessary)
  # set top level directory to source file

  library(here)

  # load reproducible environment library to get all packages with correct versions form the renv.lock file
  # install renv by calling install.packages("renv") if necessary

  library(renv)

  renv::init(here("06_Paper","COG-ED"))

  # the required packages are:
  # "bibtex", "here", "tidyverse", "bayestestR", "papaja", "lmerTest", "afex", "emmeans", "sjPlot",
  # "kableExtra", "interactions", "glmmTMB", "BayesFactor", "ggplot2", "egg", "knitr", "effectsize", and "MuMIn"

@@

@@

The Bayes Factor $BF10$ of the multi level model approached infinity.

@@

Johnson-Neyman interval: `r paste("[", round(h2c_jn.int[1], digits = 2), ", ", round(h2c_jn.int[2], digits = 2), "]", sep = "")`

Bayes Factor: $BF10=$ `r format(extractBF(h2c_BF)$bf, digits = 2)`

## Specification curve analysis:
